Objective-First Nanophotonic Design Plan

### 2012-11-26 plan/plan.tex
Some changes.
Got most of global opt theory done.

\section{The paradigm submodule}
\subsection{The local optimization paradigm}
The local optimization paradigm applies the adjoint method to solve \eq{rigorous problem statement}
    in a manner analogous to the steepest-descent strategy.
Specifically, we compute the derivative of the total field design objective with respect to $z$,
    \E{total derivative of field design objective}
        {\grad_z F = \sum_i^N \grad_z f_i(x_i),}
    and then pass 
    \E{}{Q(z) = \frac{1}{2}\norm{z-z_0}^2 + \kappa \grad_z F\cT (z-z_0)}
    to the structure submodule, for some $\kappa$.

@@

The optimization paradigm utilizes 
    the alternating directions method of multipliers\cite{ADMM} (ADMM) optimization technique, 
    which casts \eq{rigorous problem statement} in terms of the following augmented Lagrangians, 
    \E{}{\Lag(x, z, y) = \sum_i^N f_i(x_i) + 
            \frac{\rho}{2} \norm{A_i(z) x_i - b_i(z)}^2 
            +\real\left[y_i^\cT (A_i(z)x_i-b_i(z))\right] + g(z),}
    where $\rho$ is a constant scalar and 
    $y_i$ are dual variables.

ADMM obtains the solutions for $x$ and $z$ via
    \EE{}{  x_i &\gets \argmin_{x_i} \Lag(x, z, y), \quad i = 1,\ldots,N \\
            z &\gets \argmin_{z} \Lag(x, z, y), \\
            y_i &\gets y_i + \rho (A_i(x_i) z - b(x_i)), \quad i = 1,\ldots,N.}

To obtain the correct $Q(z)$ which should be passed to the structure submodule,
    we use \eq{bi-affine property} to write
    \E{}{\argmin_z \Lag = \argmin_z g(z) 
            + \sum_i^N \frac{\rho}{2} \norm{B_i(x_i) z - d(x_i)}^2 
            + \real\left[ y_i^\cT ( B_i(x_i) z - d_i(x_i))\right]}
    which means that
    \E{}{Q(z) = \sum_i^N \frac{\rho}{2} \norm{B_i(x_i) z - d(x_i)}^2 
            + \real\left[ y_i^\cT ( B_i(x_i) z - d_i(x_i))\right].}

\subsubsection{Computation of $\argmin_{x_i} \Lag$}
Updating $x_i$, which is left to the paradigm submodule,
    involves solving $\argmin_{x_i} \Lag(x, z, y)$ for all $i = 1, \ldots, N$.
This can be accomplished via
    \E{}{\grad_{x_i}\Lag = \grad_{x_i} f_i(x_i) + }

>>>>

\section{The paradigm submodule}
\subsection{The local optimization paradigm}
The local optimization paradigm applies the adjoint method to solve \eq{rigorous problem statement}
    in a manner analogous to the steepest-descent strategy.
Specifically, we compute the derivative of the total field design objective with respect to $z$,
    \E{total derivative of field design objective}
        {\grad_z F = \sum_i^N \grad_z f_i(x_i),}
    and then pass 
    \E{}{Q(z) = \frac{1}{2}\norm{z-z_0}^2 + \kappa \grad_z F^\cT (z-z_0)}
    to the structure submodule, for some $\kappa$.

@@

The optimization paradigm utilizes 
    the alternating directions method of multipliers\cite{ADMM} (ADMM) optimization technique, 
    which casts \eq{rigorous problem statement} in terms of the following augmented Lagrangians, 
    \E{}{\Lag(x, z, y) = \sum_i^N f_i(x_i) 
            + \frac{\rho}{2} \norm{A_i(z) x_i - b_i(z)}^2 
            +\real\left[y_i^\cT (A_i(z)x_i-b_i(z))\right] + g(z),}
    where $\rho$ is a constant scalar and 
    $y_i$ are dual variables. If we introduce $u_i = y_i / \rho$, then 
    \E{}{\Lag(x,z,u) = \sum_i^N f_i(x_i)
            + \frac{\rho}{2} \norm{A_i(z) x_i - b_i(z) + u_i}^2 
            - \frac{\rho}{2} \norm{u_i}^2 + g(z).}

ADMM obtains the solutions for $x$ and $z$ via
    \EE{}{  x_i &\gets \argmin_{x_i} \Lag(x, z, u), \quad i = 1,\ldots,N \\
            z &\gets \argmin_{z} \Lag(x, z, u), \\
            u_i &\gets u_i + (A_i(x_i) z - b(x_i)), \quad i = 1,\ldots,N.}

To obtain the correct $Q(z)$ which should be passed to the structure submodule,
    we use \eq{bi-affine property} to write
    \E{}{\argmin_z \Lag = \argmin_z g(z) 
            + \sum_i^N \frac{\rho}{2} \norm{B_i(x_i) z - d(x_i) + u_i}^2}
    which means that
    \E{}{Q(z) = \sum_i^N \frac{\rho}{2} \norm{B_i(x_i) z - d(x_i) + u_i}^2}

\subsubsection{Computation of $\argmin_{x_i} \Lag$}
Updating $x_i$, which is left to the paradigm submodule,
    involves solving $\argmin_{x_i} \Lag(x, z, u)$ via Newton's method for all $i = 1, \ldots, N$.
This can be accomplished via the gradient with respect to $x_i$
    \E{}{\grad_{x_i}\Lag(x, z, u) = \grad_{x_i} f_i(x_i)
                + \rho A_i(z)\T (A_i(z) x_i - b_i(z) + u_i),}
    as well as the Hessian with respect to $x_i$
    \E{}{\grad^2_{x_i}\Lag(x, z, u) = \grad^2_{x_i} f_{x_i} + \rho A_i(z)\T A_i(z),}
    which can be combined to determine the direction of a step in Newton's method,
    \E{}{\Delta x_i = - \grad^2_{x_i} \Lag^{-1} \grad_{x_i} \Lag.}

Solving $\argmin_{x_i} \Lag(x, z, u)$ from an initial $x_i$ thus proceeds by
    repeatedly computing $\Delta x_i$ and then performing a line search along that direction,
    until some convergence criterion is met, typically
    \E{}{\frac{1}{2} \grad_{x_i}\Lag\T \grad^2_{x_i} \Lag^{-1} \grad_{x_i} \Lag \le \text{error threshold}.}

\subsubsection{Relaxation of $f_i(x_i)$}
In order to compute $\Delta x_i$ we relax the design objectives, $f_i(x_i)$, to a differentiable, and convex form.
Specifically, the upper bound constraint is relaxed via
    \E{}{I_+(\beta_{ij} - |c\T_{ij} x_i|) \to -\frac{1}{t} \ln (\beta_{ij}^2 - \norm{c\T_{ij} x_i}^2),}
    where $t$ is a real positive scalar. The lower bound constraint is relaxed via
    \E{}{I_+(|c\T_{ij} x_i| - \alpha_{ij}) \to -\frac{1}{t} \ln (\real[e^{i\phi}c\T_{ij} x_i] - \alpha_{ij}),}
     where $e^{i\phi}$ is a phase factor on $c\T_{ij} x_i$.

The gradient can now be obtained as
% \footnote{
%     \EE{}{\grad_{x_i} f_i(x_i) &= \frac{1}{t(\beta_{ij}^2 - \norm{c\T_{ij} x_i}^2)} c_{ij}c\T_{ij} x_i
%                             - \frac{1}{t(\real[e^{i\phi} c\T_{ij} x_i] - \alpha_{ij})} e^{i\phi}c_{ij} \\
%                         &= \frac{1}{t} \left( \frac{c\T_{ij} x_i}{\beta_{ij}^2 - \norm{c\T_{ij} x_i}^2} 
%                             - \frac{e^{i\phi}}{\real[e^{i\phi} c\T_{ij} x_i] - \alpha_{ij}} \right)
%                         c_{ij}}
% 
%     
%     \E{}{\grad_{x_i}^2 f_i(x_i) = \frac{1}{t} \left(
%                 \frac{1}{\beta_{ij} - \norm{c\T_{ij} x_i}^2}
%                 + \frac{\norm{c\T_{ij} x_i}^2}{(\beta_{ij} - \norm{c\T_{ij} x_i}^2)^2}
%                 + \frac{1}{(\real[e^{i\phi} c\T_{ij} x_i] - \alpha_{ij})^2} \right)
%                 c_{ij} c\T_{ij}}}

    \E{}{\grad_{x_i} f_i(x_i) = \frac{s_1}{t} c_{ij}}
    where
    \E{}{s_1 = \frac{c\T_{ij} x_i}{\beta_{ij}^2 - \norm{c\T_{ij} x_i}^2} 
                - \frac{e^{i\phi}}{\real[e^{i\phi} c\T_{ij} x_i] - \alpha_{ij}},}
    and the Hessian as 
    \E{}{\grad_{x_i}^2 f_i(x_i) = \frac{s_2}{t} c_{ij} c\T_{ij}}
    where
    \E{}{s_2 = \frac{1}{\beta_{ij} - \norm{c\T_{ij} x_i}^2}
                + \frac{\norm{c\T_{ij} x_i}^2}{(\beta_{ij} - \norm{c\T_{ij} x_i}^2)^2}
                + \frac{1}{(\real[e^{i\phi} c\T_{ij} x_i] - \alpha_{ij})^2}.}

\subsubsection{Computation of $\Delta x_i$}
We now show how $\Delta x_i$ may be efficiently computed.
